The origin of cosmic-ray electrons in cluster outskirts

### 2012-01-27 paper.tex
section 3

% --- Anders's commands --- %
\newcommand{\ev}{\mathrm{eV}}
\newcommand{\gev}{\mathrm{GeV}}
\newcommand{\mev}{\mathrm{MeV}}
\newcommand{\tev}{\mathrm{TeV}}
\newcommand{\mpc}{m_{\mathrm{p}}c}
\newcommand{\mpcc}{m_{\mathrm{p}}c^2}
\newcommand{\p}{\mathrm{p}}
\newcommand{\Pp}{\mathrm{P}_\mathrm{p}}
\newcommand{\Pe}{\mathrm{P}_\mathrm{e}}
\newcommand{\pp}{p_\mathrm{p}}
\newcommand{\pe}{p_\mathrm{e}}
\newcommand{\br}{\bold{r}}
\newcommand{\e}{\mathrm{e}}
\newcommand{\ii}{\mathrm{i}}
\newcommand{\inj}{\mathrm{inj}}
\newcommand{\pd}{\partial}
\newcommand{\CR}{\mathrm{CR}}
\newcommand{\gas}{\mathrm{gas}}
\newcommand{\mr}{\mathrm}
\newcommand{\DM}{\mathrm{DM}}
\newcommand{\ISM}{\mathrm{ISM}}
\newcommand{\ICM}{\mathrm{ICM}}
\newcommand{\CMB}{\mathrm{CMB}}
\newcommand{\IC}{\mathrm{IC}}
\newcommand{\mecc}{m_\e c^2}
\newcommand{\mug}{\mathrm{\mu G}}
\newcommand{\rvir}{R_{200}}
\newcommand{\B}{\mathrm{B}}
\newcommand{\ma}{\mathrm{max}}
\newcommand{\low}{\mathrm{low}}
\newcommand{\gae}{\gamma_\mathrm{e}}
\newcommand{\gam}{\gamma}

@@

\begin{table}
\caption{Cluster sample.}
\begin{tabular}{l l l l r r r}
\hline
\hline
Cluster & sim.'s & dyn. state$^{(1)}$ & $M_{\rm vir}^{(2)}$ & $\rvir^{(2)}$ & $kT_{\rm vir}^{(3)}$ & $\Delta t$$^{(1=4)}$\\
& & & [$\rmn{M}_\odot$] & [Mpc] & [keV] & \\
\hline
1  & g8a  & CC    & $2.6\times 10^{15}$ &   2.9~~ & 13.1 \\
2  & g1a  & CC    & $1.9\times 10^{15}$ &   2.5~~ & 10.6 \\
3  & g72a & PostM & $1.6\times 10^{15}$ &   2.4~~ & 9.4  \\
4  & g51  & CC    & $1.5\times 10^{15}$ &   2.4~~ & 9.4  \\

5  & g1b  & M     & $5.2\times 10^{14}$ &   1.7~~ & 4.7  \\
6  & g72b & M     & $2.2\times 10^{14}$ &   1.2~~ & 2.4  \\
7  & g1c  & M     & $2.0\times 10^{14}$ &   1.2~~ & 2.3  \\
8  & g8b  & M     & $1.5\times 10^{14}$ &   1.1~~ & 1.9  \\
9  & g1d  & M     & $1.3\times 10^{14}$ &   1.0~~ & 1.7  \\

10 & g676 & CC    & $1.3\times 10^{14}$ &   1.0~~ & 1.7  \\
11 & g914 & CC    & $1.2\times 10^{14}$ &   1.0~~ & 1.6  \\
12 & g1e  & M     & $9.1\times 10^{13}$ &  0.93   & 1.3  \\
13 & g8c  & M     & $8.5\times 10^{13}$ &  0.91   & 1.3  \\
14 & g8d  & PreM  & $7.8\times 10^{13}$ &  0.88   & 1.2  \\
\hline
\end{tabular}  \begin{quote}
 Notes:\\ (1) The dynamical state has been classified through a combined
 criterion invoking a merger tree study and the visual inspection of the X-ray
 brightness maps. The labels for the clusters are M--merger, PostM--post
 merger (slightly elongated X-ray contours, weak cool core (CC) region developing),
 PreM--pre-merger (sub-cluster already within the virial radius), CC--cool
 core cluster with extended cooling region (smooth X-ray profile).  (2) The
 virial mass and radius are related by $M_\Delta(z) = \frac{4}{3} \pi\,
 \Delta\, \rho_\rmn{crit}(z) R_\Delta^3 $, where $\Delta=200$ denotes a
 multiple of the critical overdensity $\rho_\rmn{crit}(z) = 3 H (z)^2/ (8\pi
 G)$.  (3) The virial temperature is defined by $kT_{\rm vir} = G M_{\rm vir} \,
 \mu\, m_\p / (2 R_{\rm vir})$, where $\mu$ denotes the mean molecular weight.
\end{quote}
\label{tab:cluster_sample}
\end{table}

INSERT CLUSTER TABLE WITH DELTA T HERE, USE 100 MYR, AND THE LOG A

\subsection{CR protons}
For each SPH fluid element we attach a distribution function of CR protons. It is represented by a one-dimensional isotropic distribution function \footnote{The three dimensional distibution function is given by $4\pi \int f(p) p^ 2 \dd p$.} given by
\begin{equation}
  \label{eq:f_p}
  f_\p(p_\p) = \frac{\dd^2 N_\p}{\dd p_\p\,\dd V} = 
  C\, p_\p^{-\alpha}\,\theta(p_\p-q)\,, 
\end{equation}
and $p_\p = P_\p/m_\p c$, where we have normalized the proton momentum
$P_\p$ with the proton mass $m_\p$.  Here $q$ is the mass normalized
momentum cutoff, $\alpha$ the spectral index, and $C$ the
normalization of the distribution function in units of density.

@@

>>>>

% --- Anders's commands --- %
\newcommand{\ev}{\mathrm{eV}}
\newcommand{\gev}{\mathrm{GeV}}
\newcommand{\mev}{\mathrm{MeV}}
\newcommand{\tev}{\mathrm{TeV}}
\newcommand{\mpc}{m_{\mathrm{p}}c}
\newcommand{\mpcc}{m_{\mathrm{p}}c^2}
\newcommand{\p}{\mathrm{p}}
\newcommand{\Pp}{\mathrm{P}_\mathrm{p}}
\newcommand{\Pe}{\mathrm{P}_\mathrm{e}}
\newcommand{\pp}{p_\mathrm{p}}
\newcommand{\pe}{p_\mathrm{e}}
\newcommand{\br}{\bold{r}}
\newcommand{\e}{\mathrm{e}}
\newcommand{\ii}{\mathrm{i}}
\newcommand{\inj}{\mathrm{inj}}
\newcommand{\pd}{\partial}
\newcommand{\CR}{\mathrm{CR}}
\newcommand{\gas}{\mathrm{gas}}
\newcommand{\mr}{\mathrm}
\newcommand{\DM}{\mathrm{DM}}
\newcommand{\ISM}{\mathrm{ISM}}
\newcommand{\ICM}{\mathrm{ICM}}
\newcommand{\CMB}{\mathrm{CMB}}
\newcommand{\IC}{\mathrm{IC}}
\newcommand{\mecc}{m_\e c^2}
\newcommand{\mug}{\mathrm{\mu G}}
\newcommand{\rvir}{R_{200}}
\newcommand{\B}{\mathrm{B}}
\newcommand{\ma}{\mathrm{max}}
\newcommand{\low}{\mathrm{low}}
\newcommand{\gae}{\gamma_\mathrm{e}}
\newcommand{\gam}{\gamma}
\newcommand{\tend}{t_\rmn{end}}

@@

\begin{table}
\caption{Cluster sample.}
\begin{tabular}{l l l l r r r}
\hline
\hline
Cluster & sim.'s & state$^{(1)}$ & $M_{\rm vir}^{(2)}$ & $\rvir^{(2)}$ & $kT_{\rm vir}^{(3)}$ & $\Delta t$$^{(4)}$\\
& & & [$\rmn{M}_\odot$] & [Mpc] & [keV] & \\
\hline
1  & g8a  & CC    & $2.6\times 10^{15}$ &   2.9~~ & 13.1 & 1.127 \\
2  & g1a  & CC    & $1.9\times 10^{15}$ &   2.5~~ & 10.6 & 1.127 \\
3  & g72a & PostM & $1.6\times 10^{15}$ &   2.4~~ & 9.4  & 100 Myr \\
4  & g51  & CC    & $1.5\times 10^{15}$ &   2.4~~ & 9.4  & 1.127 \\

5  & g1b  & M     & $5.2\times 10^{14}$ &   1.7~~ & 4.7  & 1.127 \\
6  & g72b & M     & $2.2\times 10^{14}$ &   1.2~~ & 2.4  & 100 Myr \\
7  & g1c  & M     & $2.0\times 10^{14}$ &   1.2~~ & 2.3  & 1.127 \\
8  & g8b  & M     & $1.5\times 10^{14}$ &   1.1~~ & 1.9  & 1.127 \\
9  & g1d  & M     & $1.3\times 10^{14}$ &   1.0~~ & 1.7  & 1.127 \\

10 & g676 & CC    & $1.3\times 10^{14}$ &   1.0~~ & 1.7  & 1.049 \\
11 & g914 & CC    & $1.2\times 10^{14}$ &   1.0~~ & 1.6  & 1.049 \\
12 & g1e  & M     & $9.1\times 10^{13}$ &  0.93   & 1.3  & 1.127 \\
13 & g8c  & M     & $8.5\times 10^{13}$ &  0.91   & 1.3  & 1.127 \\
14 & g8d  & PreM  & $7.8\times 10^{13}$ &  0.88   & 1.2  & 1.127 \\
\hline
\end{tabular}  \begin{quote}
 Notes:\\ (1) The dynamical state has been classified through a combined
 criterion invoking a merger tree study and the visual inspection of the X-ray
 brightness maps. The labels for the clusters are M--merger, PostM--post
 merger (slightly elongated X-ray contours, weak cool core (CC) region developing),
 PreM--pre-merger (sub-cluster already within the virial radius), CC--cool
 core cluster with extended cooling region (smooth X-ray profile).  (2) The
 virial mass and radius are related by $M_\Delta(z) = \frac{4}{3} \pi\,
 \Delta\, \rho_\rmn{crit}(z) R_\Delta^3 $, where $\Delta=200$ denotes a
 multiple of the critical overdensity $\rho_\rmn{crit}(z) = 3 H (z)^2/ (8\pi
 G)$.  (3) The virial temperature is defined by $kT_{\rm vir} = G M_{\rm vir} \,
 \mu\, m_\p / (2 R_{\rm vir})$, where $\mu$ denotes the mean molecular weight.
 (4) Time difference between output snapshots; in units of Myr for g72, and 
 remaining clusters show the ratio of the cosmological scalefactor between 
 two snapshots.
\end{quote}
\label{tab:cluster_sample}
\end{table}

\section{Method}
In this section we outline the formalism that we use to derive the CR
electron spectra that builds up during the structure formation of
galaxy clusters, and the expected synchrotron emission from in galaxy
cluster that is undergoing a merger at low redshift.

Our scheme is summerized by:
\begin{itemize}
\item derive CR proton distribution function from each simulation output at different time $t$
\item calculate injected CR proton population between snapshots 
\item convert injected protons to injected electrons
\item evolve each injected CR electron population to a later time $\tend$ by
  accounting for losses (Coulomb, inverse Compton, and adiabatic)
\item add up the CR electron distibution for all SPH particles at time $\tend$
\item re-accelerate CR electron distribution function at time $\tend$
  using typical values for a merging shock in cluster outskirts
\item calculate the synchrotron radio emission from radio relic

\end{itemize}

\subsection{CR protons}
For simplicity we have attach a distribution function of CR protons to
each SPH fluid element. It is represented by a one-dimensional
isotropic distribution function \footnote{The three dimensional
  distibution function is given by $4\pi \int f(p)\, p^2\, \dd p$.}
given by
\begin{equation}
  \label{eq:f_p}
  f_\p(p_\p) = \frac{\dd^2 N_\p}{\dd p_\p\,\dd V} = 
  C\, p_\p^{-\alpha}\,\theta(p_\p-q)\,, 
\end{equation}
and $p_\p = P_\p/m_\p c$, where we have normalized the proton momentum
$P_\p$ with the proton mass $m_\p$. Here $q$ is the mass normalized
momentum cutoff, $\alpha$ the spectral index, and $C$ the
normalization of the distribution function in units of density.

@@

CONTINUE FROM HERE
